---
title: "day_2_notes ~ beta_binom_analysis"
author: "Dane Dewees"
date: "January 11, 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

**Question:** We flip an odd-looking coin 100 times, and get 65 heads. What is it’s true* probability of heads?

## What is True? ##

The long-run proportion of heads (if we flipped it a lot). 


## What prior to use? ## 

We'll use $\alpha - \beta = 1$: a flat prior. 


## Analysis ##

Know that posterior distribution on $P$, the true probs of heads, 
is Beta($\alpha + z$, $\beta + n - z$). 

Here $z=65$ and $n=100$.


We will make a plot of the density funciton

```{r bayes}

z <- 65
n <- 100

prior_alpha <- 1
prior_beta <- 1


post_alpha <- prior_alpha + z

post_beta <- prior_beta + n - z

# look at the theta at 1000 points
x <- seq(0, 1, length.out=1000)

dens <- dbeta(x, shape1= post_alpha, shape2 = post_beta)


plot(x, dens, type='l',
     xlab='probs of heads', ylab = 'posterior density')
```



## Is it reasonable that $\theta=1/2$?

It looks like not: the posterior probs that $P \le 1/2$ is `r pbeta(1/2, shape1=post_alpha, shape2=post_beta)`.


## Best guess at $\theta$?

We'll take the max a pos



